Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-31 R0V0.tex
Start to write about diagonal dominance and the search for appropriate basis

>>>>

Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation. There is no reason for the dimension of these components (matrices) to be small enough. However, by employing an appropriate choice of the basis, the dimension of the matrix can be smaller \cite{AhmadiHall2016}.
